\Huge ACM and Climate Change

### 2019-05-14 rewrite.tex
Start at a rewrite.

\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{multicol}

@@

ACM's vibrant conference culture has a dark side: it contributes
significantly to climate change.

>>>>

\usepackage{fullpage}
\usepackage{times}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{multicol}

@@

ACM's vibrant conference culture has a dark side: it contributes
significantly to climate change. What should we do about it?

\bigskip{}

Experts say that human civilization must reduce CO2 emissions by 40\%
by 2030. To do that, we all need to tighten our CO2-emitting belts. For
academic computer scientists, from what activity should the CO2 reduction come?
Look no further than our professional conferences. Air
travel is CO2 heavy, on a per-capita basis. A few trans-oceanic trips
is XXX CO2. Wow!

As responsible scientists wanting to do our part to sustain our
environment, should we eliminate (most) conferences, and thereby the
travel to organize and attend them? Doing so could impose a high cost
on scientific progress. Science is a fundamentally social process. The
conference system leverages that, accelerating research through easy
interaction, direct dissemination of results, and network building to
further new work. It works well enough that conferences are
proliferating and attendance is on the rise. So the challenge is: How
do we weigh the benefits to science of conferences against their
attendant CO2 (and other) costs? This seems like an extremely
difficult question to answer.

But not so fast: such difficult questions are answered all the time
through the magic of markets. By mapping choices to currency amounts,
markets facilitate individual valuation of costs and benefits across
vastly different activities, like the cost of flying and staying in a
hotel vs. the benefit of attending a scientific meeting. If the former
was too high, we would not do the latter. To facilitate answers to
difficult questions about CO2 costs, many are advocating CO2-centered
markets, by placing a dollar cost on CO2 emissions. California has
already done this. In a world in which CO2 had a cost, air travel
would be more expensive because flyers would have to bear its CO2
cost, too. The result would place downward pressure on conferences
that were CO2-inefficient for their attendees.

There’s no global market for CO2 just yet, so does that mean we should
do nothing until there is one? Not necessarily. We can start to impose
the discipline on ourselves right now.

First, we can recognize there is an emerging price for CO2, which is
the price of CO2 offsets. [Explain what they are.]

With a CO2 cost in hand, we can establish an acceptable baseline CO2
cost for an event. This baseline could be established by analyzing
[...] Planners can track this cost according to the CO2 footprint of
their attendees. [...]

\hrule
\clearpage

\texdtbf{OLD STUFF HERE}
